### 2020-01-21 paper/sex_selection_spacing-ver3.tex
Reorganizing introduction

@@

% [Why India?]
India is a particularly compelling case with its long history of male preference, 
especially in the northern states \citep{Kishor1993,murthi95,arnold98}.
Mortality risk is higher for females than males for most ages groups, resulting in
an almost continuous increase in India's overall ratio of males to females 
over the last century \citep{dyson01,Navaneetham2011,Bongaarts2015}.
Differential stopping behavior is widespread, with an additional child more likely the
fewer sons a family has 
\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.%
\footnote{
Other countries show a similar pattern
\citep[see, for example,][]{larsen98,filmer09,Altindag2016}.
}
Furthermore, fertility has declined substantially, to the point where it is now at, or even 
below, replacement in some areas 
\citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
The combination of falling fertility, strong son preference, and expanding access to 
prenatal sex determination has lead to dramatic increases in the males-to-females ratio at 
birth over the last three decades
\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2009a,Guilmoto2012,Bongaarts2013,Portner2015b,Jayachandran2017}.

>>>>

% [Why India?]
India has a long history of pro-male preference \citep{Kishor1993,murthi95,arnold98}.
Mortality risk is higher for females than males for most ages groups, resulting in
an almost continuous increase in the ratio of males to females over the last century
 \citep{dyson01,Navaneetham2011,Bongaarts2015}.
Differential stopping behavior is widespread, with an additional child more likely the
fewer sons a family has 
\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.
The duration to the next birth is also shorter with fewer sons, likely contributing
to the higher mortality and morbidity risk for girls
\citep{Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,Maitra2008,Makepeace2008,
Jayachandran2011,Kumar2016,Jayachandran2017a,Ghosh2018}.
Furthermore, India's total fertility rate has declined substantially and is now below 
replacement in some areas [TK more precision] 
\citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
The combination of falling fertility, strong son preference, and expanding access to 
prenatal sex determination dramaticly increased the males-to-females ratio at 
birth over the last three decades
\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2009a,Guilmoto2012,
Bongaarts2013,Portner2015b,Jayachandran2017}.

Highlights:
- changes in spacing overall
- much longer spacing with girls
- biases in TFR
- effects on mortality

@@
